Engineering the Servo Web Browser Engine using Rust

### 2015-10-23 icse16-servo/abstract.tex
Additional ICFP comment

Servo is a project started at Mozilla Research to build a new web browser engine that
preserves the capabilities of these other browser engines but also both takes 
advantage of the recent trends in parallel hardware and is more memory-safe.
We use a new language, Rust, that provides us a similar level of control of the underlying
system to \Cplusplus{} but which builds on many concepts familiar to the functional programming
community, forming a novelty --- a useful, safe systems programming language.

>>>>

Servo is a project started at Mozilla Research to build a new web browser engine that
preserves the capabilities of these other browser engines but also both takes 
advantage of the recent trends in parallel hardware and is more memory-safe.
We use a new language, Rust, that provides us a similar level of control of the underlying
system to \Cplusplus{} but which builds on many concepts familiar to the functional programming
community.
